---
title: "Presentation about Dogs"
author: "Revathy Ponnambalam"
date: "2022/10/01"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle

#Dogs are the best pet animals 
## cats and birds are other famous pet animals 
---
class: center, middle

# Breeds of dogs 
there are more breeds of dogs present aroundthe world and the top 7 famous breeds are as follows:

#### Golden retriever.
#### Labrador retriever.
#### French bulldog.
#### Beagle.
#### German shepherd dog.
#### Poodle.
#### Bulldog
---
class: center, middle

# How many dogs will a person come across in his life??

```{r, echo= FALSE }
print("everyone would have come across more than 10 dogs in their life")
print("Golden Retriever are the cutest")
print("I don't think anyone is who has not seen a dog")
```


---

# Which breed lives the longest 

## Jack Russell Terriers had life expectency of 12.72 years, followed by Yorkshire Terriers (12.54 years), Border Collies (12.10 years), and Springer Spaniels (11.92 years)

--


 I wish my dog lives the longest too
--


---

# How many dogs have I owned 
## I have owned two dogs till now and I really miss my dog alot. 

```{r}
first <- 1
second <- 2 
total <- first + second 

print(total)
```
---

class: center, middle

# Thanks!

